
---
title: "Analysis"
date: "4/8/2022"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


```{r}
dat <- read.csv("~/Documents/BGSU/Spring 2022/stat 5080 Experimental design/Project/data.csv", stringsAsFactors = T,fileEncoding = 'UTF-8-BOM')
dat$difficulty <- relevel(dat$difficulty, "50cc")
```

# ANOVA
```{r}
aov_out <- aov(formula = time ~ numPlayers*difficulty*sound + participant,
               data = dat)
summary(aov_out)
```

# Assumption Checking
```{r echo=FALSE}
# svg("C:/Users/hadamul/OneDrive/Graduate school/Semester 4/Experimental Design/Experimental-Design-Final-Project/Plots/qq.svg",
#     width = 7.291667, height = 4.500000)
qqnorm(aov_out$residuals)
qqline(aov_out$residuals)
# dev.off()
```

```{r}
# svg("C:/Users/hadamul/OneDrive/Graduate school/Semester 4/Experimental Design/Experimental-Design-Final-Project/Plots/factorEqVar.svg",
#     width = 7.291667, height = 4.500000)
par(mfrow = c(2,2),
    mar = c(2,0,0,0),
    mgp = c(0,.5,0),
    omi = c(0,.25,0,0))
plot(x = dat$numPlayers, y = aov_out$residuals,
     xlab = "", ylab = "Residuals")
plot(x = dat$difficulty, y = aov_out$residuals,
     xlab = "", ylab = "", yaxt = "n")
plot(x = dat$sound, y = aov_out$residuals,
     xlab = "", ylab = "Residuals")
plot(x = dat$participant, y = aov_out$residuals,
     xlab = "", ylab = "Residuals", yaxt = "n")
# dev.off()
```


```{r echo=FALSE}
# svg("C:/Users/hadamul/OneDrive/Graduate school/Semester 4/Experimental Design/Experimental-Design-Final-Project/Plots/Res_v_FitEqVar.svg",
#     width = 7.291667, height = 4.500000)
plot(aov_out$fitted.values,aov_out$residuals,xlab="Fitted Lap Times",ylab="Residuals",
     main="Residuals vs. Fitted Lap Times")
abline(h=0)
# dev.off()
```


```{r echo=FALSE}
# svg("C:/Users/hadamul/OneDrive/Graduate school/Semester 4/Experimental Design/Experimental-Design-Final-Project/Plots/ResidualIndex.svg",
#     width = 7.291667, height = 4.500000)
plot(aov_out$residuals,ylab="Residuals",type="l",
     main="Residuals vs. Index", xlim = c(1,72))
# dev.off()
```

```{r echo=FALSE}
res_ind_df <- data.frame(index = 1:length(aov_out$residuals),
                          res = aov_out$residuals)
res_ind_lm1 <- lm(res~index, res_ind_df[1:18,])
res_ind_lm2 <- lm(res~index, res_ind_df[(18+1):(18*2),])
res_ind_lm3 <- lm(res~index, res_ind_df[(18*2+1):(18*3),])
res_ind_lm4 <- lm(res~index, res_ind_df[(18*3+1):(18*4),])
# svg("C:/Users/hadamul/OneDrive/Graduate school/Semester 4/Experimental Design/Experimental-Design-Final-Project/Plots/ResidualIndexBlock.svg",
#     width = 7.291667, height = 4.500000)
plot(aov_out$residuals,ylab="Residuals",type="l",
     main="Residuals vs. Index", xlim = c(1,72))
abline(v= 18)
abline(v= 18*2)
abline(v= 18*3)
clip(1, 18, -100, 100)
abline(res_ind_lm1, xlim = 1:18)
clip(18, 18*2, -100, 100)
abline(res_ind_lm2, xlim = 1:18)
clip(18*2, 18*3, -100, 100)
abline(res_ind_lm3, xlim = 1:18)
clip(18*3, 18*4, -100, 100)
abline(res_ind_lm4, xlim = 1:18)
# dev.off()
```

```{r}
MASS::boxcox(aov_out)
```

Plot Interpretation: For the Box-Cox transformation, a λ value of 1 is equivalent to using the original data. from the Box-Cox plot, we can clearly see that optimum $\lambda$ is close to 1. Therefore no transformation is required.
from the Box-Cox plot, we can clearly see that the 95% confidence interval includes 1 in the range therefore, no transformation is required for our data





# Interaction
```{r}
interaction.plot(x.factor = dat$sound, trace.factor = dat$difficulty, response = dat$time)
interaction.plot(x.factor = dat$difficulty, trace.factor = dat$sound, response = dat$time,
                 fixed = T,)
```


# Check the interactions charts for any interaction that may be hidden by the error

# Looking at the Tukey comparisons for difficilty
```{r}
TukeyHSD(aov_out, "difficulty",ordered = T)
bruh <- TukeyHSD(x = aov_out,
                 which = "difficulty",
                 ordered = T)$difficulty %>% 
  apply(2,function(i) as.numeric(i)) %>% as.data.frame()
difficultyTukey <- cbind(comparison = c("100cc->150cc",
                                        "50cc->150cc",
                                        "50cc->100cc"),
                         bruh)
```   
- 150cc is about 12.3 seconds faster than 100cc
- 100cc is about 4.8 seconds faster than 50cc
- 150cc is about 13.3 seconds faster than 50cc

```{r}
ggplot(data = difficultyTukey) +
  geom_bar(mapping = aes(x =  comparison, y = diff), stat="identity") +
  geom_errorbar(mapping = aes(x = comparison, ymin = lwr, ymax = upr)) +
   coord_flip()
```


# A case for the polynomial comparison for difficulty

Normal everyday players see this as 3 distinct levels, but modders (people who access and mod the game files) knows that there is a range of values that controls the speed of the carts, so to them, there are a range of values that one can use for the "difficulty".






50cc 
speed <- 10


100cc 
speed <- 20


150cc 
speed <- 30


speed <- 1
speed <- 15
speed <- 300000